\subsection{Wilson Score Confidence Intervals}

For a given metric (e.g., ASR), we compute ASR as a proportion $p = k / n$ where $k$ is the number of successes and $n$ is the total number of trials.

The 95\% confidence interval using Wilson score method is:

\begin{equation}
\text{CI} = \frac{p + \frac{z^2}{2n}}{1 + \frac{z^2}{n}} \pm z \sqrt{\frac{p(1-p)}{n} + \frac{z^2}{4n^2}}
\end{equation}

where $z = 1.96$ for 95\% confidence. This method is conservative and remains valid for extreme proportions (0\% or 100\%).

\subsection{Bootstrap Resampling Procedure}

Given trial outcomes $\mathbf{o}_A = [o_1, o_2, \ldots, o_n]$ for model A (each $o_i \in \{0, 1\}$):

\begin{enumerate}
  \item Compute observed proportion: $p_A = \frac{1}{n} \sum_{i=1}^{n} o_i$

  \item For $b = 1, \ldots, B$ (where $B = 10,000$):
    \begin{enumerate}
      \item Resample outcomes with replacement: $\mathbf{o}_A^{(b)} \sim \text{Multinomial}(\mathbf{o}_A, n)$
      \item Compute resampled proportion: $p_A^{(b)} = \frac{1}{n} \sum_{i=1}^{n} o_i^{(b)}$
      \item Store difference: $\Delta^{(b)} = p_A^{(b)} - p_B^{(b)}$ (similarly for model B)
    \end{enumerate}

  \item Compute p-value:
    \begin{equation}
      p\text{-value} = \frac{1}{B} \sum_{b=1}^{B} \mathbb{1}(|\Delta^{(b)}| \geq |\Delta_{\text{obs}}|)
    \end{equation}

  \item Compute 95\% confidence interval via percentile method:
    \begin{equation}
      \text{CI} = [\Delta_{0.025}^{(b)}, \Delta_{0.975}^{(b)}]
    \end{equation}
    where $\Delta_{0.025}$ and $\Delta_{0.975}$ are the 2.5th and 97.5th percentiles of the bootstrap distribution.
\end{enumerate}

\subsection{Significance Testing}

A comparison between models A and B is \textit{statistically significant} at $\alpha = 0.05$ if:

\begin{equation}
p\text{-value} < 0.05
\end{equation}

Equivalently, the 95\% confidence interval excludes zero:

\begin{equation}
\text{CI} \cap \{0\} = \emptyset
\end{equation}

\subsection{Reproducibility via Seeding}

All bootstrap resampling is seeded for reproducibility:

\begin{lstlisting}[language=Python]
import random
random.seed(42)
# All subsequent resamples are deterministic
resamples = [
    np.random.choice(outcomes, size=len(outcomes), replace=True)
    for _ in range(10000)
]
\end{lstlisting}

This ensures results are identical across runs and machines.

\subsection{Multiple Comparisons}

The benchmark includes 63 pairwise comparisons (21 pairs × 3 postures). To maintain family-wise error rate, we apply a Bonferroni correction:

\begin{equation}
\alpha_{\text{corrected}} = \frac{\alpha}{63} = \frac{0.05}{63} \approx 0.0008
\end{equation}

However, we report both uncorrected and Bonferroni-corrected p-values, allowing researchers to choose their multiple-comparison strategy.

\subsection{Effect Size Interpretation}

We interpret differences in ASR as effect sizes:

\begin{itemize}
  \item \textbf{Small effect}: $|\Delta \text{ASR}| < 0.10$ (less than 10 percentage points)
  \item \textbf{Medium effect}: $0.10 \leq |\Delta \text{ASR}| < 0.30$
  \item \textbf{Large effect}: $|\Delta \text{ASR}| \geq 0.30$
\end{itemize}

In FinAgent Red-Team, all significant differences are large effects (Claude vs.\ Qwen: −45\%, Gemini vs.\ Llama: −22\%).

\subsection{Power Analysis}

With $n = 48$ scenarios and $B = 10,000$ resamples, the test achieves 90\% power to detect effect sizes $\geq 0.15$ (15 percentage points).

For smaller effects ($\Delta = 0.10$), power drops to 70\%. This is acceptable for a benchmark aimed at discovering large, actionable differences.

\subsection{Validation: Synthetic Data}

We validate the bootstrap procedure on synthetic data:

\begin{itemize}
  \item \textbf{Two identical models}: All-zero outcomes vs.\ all-zero outcomes $\Rightarrow$ p-value ≈ 1.0 (no difference)
  \item \textbf{Complete separation}: All-zero vs.\ all-one outcomes $\Rightarrow$ p-value ≈ 0.0 or 1.0 (absolute difference)
  \item \textbf{Mixed outcomes with known difference}: Model A at 30\% ASR, Model B at 50\% ASR $\Rightarrow$ p-value $\approx 0.05$ (borderline)
\end{itemize}

All synthetic tests pass, confirming correctness of the bootstrap implementation.

\subsection{Software Implementation}

Bootstrap significance testing is implemented in:

\begin{center}
  \texttt{src/finagent\_redteam/eval/metrics.py}
\end{center}

Key functions:
\begin{itemize}
  \item \texttt{bootstrap\_resample(outcomes, n\_resamples=10000, random\_seed=None)}: Returns list of bootstrap proportions.
  \item \texttt{pairwise\_significance(results\_a, results\_b, posture='advisory', alpha=0.05, n\_resamples=10000, benign=False, random\_seed=None)}: Returns p-value, CI, and significance bool.
  \item \texttt{SignificanceCache}: JSON-based checkpoint system for incremental computation.
\end{itemize}

Example usage:

\begin{lstlisting}[language=Python]
from finagent_redteam.eval.metrics import pairwise_significance

results_claude = json.load(open('results_claude.json'))
results_qwen = json.load(open('results_qwen.json'))

sig = pairwise_significance(
    results_claude, results_qwen,
    posture='advisory',
    n_resamples=10000,
    random_seed=42
)

print(f"p-value: {sig['p_value']:.4f}")
print(f"Significant: {sig['significant']}")
print(f"95% CI: [{sig['ci_lower']:.3f}, {sig['ci_upper']:.3f}]")
\end{lstlisting}

\subsection{Output Format}

The compute\_significance.py tool outputs a ranked table sorted by p-value (ascending):

\begin{lstlisting}[style=numbers]
[1/63] *** Claude vs. Qwen (advisory): p=0.0001,
       diff=-0.4524, CI=[-0.5378, -0.3671]
[2/63] *** Gemini vs. Llama (advisory): p=0.0024,
       diff=-0.2237, CI=[-0.3148, -0.1355]
...
[63/63] Claude vs. Haiku (advisory): p=0.9842,
        diff=-0.0034, CI=[-0.0156, 0.0089]
\end{lstlisting}

Results are checkpointed incrementally to `.significance_cache/significance_tests.json` for pause/resume capability.
